---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

```{r, echo=TRUE}
activityData <- read.csv("~/GitHub/RepData_PeerAssessment1/activity.csv")

# date data to date format
activityData$date <- as.Date(activityData$date)
```

## What is mean total number of steps taken per day?

```{r, echo=TRUE}
# 1. Calculate the total number of steps taken per day
TotalStepsPerDay <- aggregate(steps ~ date, activityData, sum, na.action = na.omit)

# 2. Make a histogram of the total number of steps taken each day
hist(TotalStepsPerDay$steps, xlab = "Total number of steps taken per day", main = "Total number of steps taken per day")

# 3. Calculate and report the mean and median of the total number of steps taken per day

MeanStepsPerDay <- aggregate(steps ~ date, activityData, mean, na.action = na.omit)
MedianStepsPerDay <- aggregate(steps ~ date, activityData, median, na.action = na.omit)
```

The mean number of steps per day is:
```{r}
MeanStepsPerDay
```

The median number of steps per day is:
```{r}
MedianStepsPerDay
```

## What is the average daily activity pattern?

```{r}
# calculate average steps by interval (all days)
AverageStepsAllDays <- aggregate(steps ~ interval, activityData, mean, na.action = na.omit)

# plot line chart 
plot(AverageStepsAllDays$interval, AverageStepsAllDays$steps, xlab = "Intervals (5-minutes)", ylab = "Average number of steps", main = "Average number of steps by interval" , type = "l")
```


## Imputing missing values

The number of NAs is:
```{r}
# calculate NAs
sum(is.na(activityData$steps))
```

Strategy to replace NAs with median value for that interval:

```{r}
#create copy of original data to modify
activityDataComplete <- activityData

# replace NAs with median steps for same day
activityDataComplete$steps[is.na(activityDataComplete$steps)] <- activityDataComplete$steps[MedianStepsPerDay$date == activityDataComplete$date]
```


## Are there differences in activity patterns between weekdays and weekends?

```{r}

```

